---
title: 'Task 2: Parameter Estimation- Wild Fish Catch'
author: "Laurel Wee"
date: "3/6/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

```{r}
# Download and read in `fish_catch.csv` data from https://drive.google.com/file/d/1sKjDqxbpWD7vd7Kt4tBNpl6pHEf_LnIe/view?usp=sharing
fish_catch <- read.csv(here("data","fish_catch.csv")) %>% 
  slice(-(1:4)) %>% # Omit the first and last 4 rows of non-numeric data
  head(-4) %>% 
  rename("year"="World.Wild.Fish.Catch.and.Farmed.Fish.Production..1950.2012","wild_catch"="X","farmed_fish"="X.1","total_fish"="X.2") # Rename columns

# Check the class of `year` variable
# class(fish_catch$year)
# Outcome: Character

# Make a subset of data for wild caught fish counts and make new year column, data frame will be used to make an equation so values must be numeric
fish_wild<- fish_catch %>% 
  mutate(year = as.numeric(year)) %>% # Change `year` to numeric
  mutate(year_eq = ((year)-1950)) %>%  # Create new column with first year 1950 =0 
  select(year_eq, wild_catch) %>% 
  mutate(wild_catch=as.numeric(wild_catch)) # Make sure that the `wild_catch` values are numeric
# Make sure that the new year column `year_eq` is numeric
# class(fish_wild$year_eq) 
# Outcome: Numeric
```

### Part a: Exploratory graph of Wild Catch over Time
```{r}

#Plot exploratory visualization of the `wild_catch` vs `year_eq` and the `log(wild_catch)` vs `year-eq`
ggplot(data = fish_wild, aes(x = year_eq, y = wild_catch)) +
  geom_point() +
  labs(x = "Year", y = "Wild Caught Fish")

ggplot(data = fish_wild, aes(x = year_eq, y = log(wild_catch))) +
  geom_point() +
  theme_minimal() +
  labs(x = "Year", y = "ln(wild caught fish)")
```
### Part b: Wild Catch over Time trand

The graphs shown above are logistic.

$P(t)=\frac{K}{1+Ae^{-kt}}$


```{r}
fish_exp <- fish_wild %>% 
  mutate(ln_wild = log(wild_catch))

# Model linear to get *k* estimate (the slope of this linear equation is an estimate of the growth rate constant):
lm_k <- lm(ln_wild ~ year_eq, data = fish_exp)
lm_k

#k ~ 0.025
# K ~ 93
# (93-17)/17= ~4.5
```
- $K$ is the carrying capacity which is ~ 93 (million)
- $A$ is $\frac{K-P_0}{P_0}$  ${P_0} = 17$  $\frac{93-17}{17} = 4.5$ (million)
- $k$ is the growth rate constant found above $k= 0.025$



### Part c: Parameters for Model describing Wild Catch over time
#### Using nonlinear least squares
```{r}
#Using the predicted initial estimates from part b, do a nonlinear least squares
fish_nls <- nls(wild_catch ~ K/(1 + A*exp(-r*year_eq)),
              data = fish_wild,
              start = list(K = 93, A = 4.5, r = 0.025),
              trace = TRUE
              )

summary(fish_nls)

# Use broom:: functions to get model outputs in tidier format: 
model_out <- broom::tidy(fish_nls) # Use View(model_out) to see the tidy model output.

p_predict <- predict(fish_nls)

# Bind predictions to original data frame:
fish_complete <- data.frame(fish_wild, p_predict)
```
### Part d: Original data compared to model output

```{r}
# Plot them all together:
ggplot(data = fish_complete, aes(x = year_eq, y = wild_catch)) +
  geom_point() +
  geom_line(aes(x = year_eq, y = p_predict)) +
  theme_minimal()
```

