---
title: 'Task 3: Bootstrapped Confidence Interval for Proportions'
author: "Laurel Wee"
date: "3/7/2021"
output: 
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  results = FALSE)
library(tidyverse)
library(boot)
library(patchwork)
```

### Part a: Sample Vector, Proportions and 10k Bootstraped Samples
#### Create sample vector, proportions, and find 10,000 bootstrap samples for queer-gendered students that responded that they experienced hositle or exlusionary cconduct at UCSB.
```{r}
#male=628, female= 1230, genderqueer=36, transgener=7
# Create data frame where 22 out of 36 queergender students said they'd experienced misconduct, 1 yes experienced 0 is a no response
conduct <-c(rep(1,22), rep(0,14))
df <- data.frame(conduct)

# Get 95% CI for t-distribution
t.test(df$conduct)

# Create a function to find the proportion/mean
proportion_fun <- function (x,i) {mean(x[i])}

conduct_nc <- df$conduct

conductboot_10k <- boot(conduct_nc, 
                 statistic = proportion_fun, 
                 R = 10000)
# conductboot_10k$t0 
# Outcome: 0.6111111 which matches our 61%
conductboot_10k_df <- data.frame(bs_mean = conductboot_10k$t)
```

### Part b: Histogram of Bootstraped Proportions

```{r}
# The histogram of the original sample:
#p1 <- ggplot(data = df, aes(x = conduct)) +
  #geom_histogram()

# Histogram of 10000 bootstrap sample means:
p2 <- ggplot(data = conductboot_10k_df, aes(x = bs_mean)) +
  geom_histogram()

p2
```

### Part c: Confidence Interval and Conclusion

```{r}
boot.ci(conductboot_10k, conf = 0.95)
```

For a 95% confidence interval we expect 95 out of 100 calculated confidence intervals will contain the actual proportion of queer-gender students that experienced an exclusionary, hostile or intimidating experience at UCSB. 95 of 100 calculated proportions will fall between 0.44 and 0.78, our original data was a proportion of 0.61.

#### Data Citation
2014 UCSB Campus Climate Project Final Report. Rankin & Associates Consulting. http://campusclimate.ucop.edu/_common/files/pdf-climate/ucsb-full-report.pdf


